---
title: "Comparing Disney Films"
author: "Yuhaniz, Siya, Cole, Jonathan"
date: "11/25/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library("knitr")
source("scripts/chart3.R")
source("scripts/chart2.R")
source("scripts/chart1.R")
source("scripts/summary_info.R")
source("scripts/summary_table.R")
movies <- read.csv("data/disney_movies.csv", stringsAsFactors = FALSE)
```
## Introduction

Our domain of interest is entertainment so in this report, we'll be studying a 
data set comparing all of the movies made by Disney. We are interested in 
exploring the domain of entertainment because it is a very broad field with lots 
of available data in part due to the rise of streaming services. This data set 
includes all Disney movies up to 2016. It can be found [here](https://www.kaggle.com/prateekmaj21/disney-movies?select=disney_movies.csv).
We want to study this data to see what types of movies are the most successful 
in terms of grossing amount. These types of studies help Disney plan future 
films in terms of the genre, ratings etc. the film should stick to.

## Summary Info
```{r echo=FALSE, include=FALSE}
summary <- summary_info(movies)
```
This data displays a few aspects of Disney movies. Such as the release dates, 
genre, MPAA rating, total gross income and inflation adjusted gross income. In 
this data the highest grossing movie is `r summary$Highest_Gross_Movie`. Also, 
the lowest grossing movies would be the movies `r summary$Lowest_Gross_Movies`.
With this being said, the most common genre from the data are 
`r summary$Most_Common_Genre` and the most common release date year would be 
`r summary$Most_Common_Release_Year`. Finally, in this data it displays 
`r summary$Total_Movies` different movies.

## Summary Table
```{r echo=FALSE}
summary_table(maovies)
```

This table shows 10 Disney movies with the average inflation gross income of 
each movie. Included with this is the genre of each of these movies and the 
MPAA rating. This demonstrates if the movie genre and the MPAA affects the 
inflation gross income. 

## What trends do we see between the yearly gross of Disney movies over time?

This chart was intended to show the relationship between the yearly gross of 
Disney movies, comparing the inflation adjusted gross and total gross, over time 
from 1937 to 2016. We made it to see which years made the most movies gross.

```{r plot3, echo=FALSE, fig.width= 20}
make_1st_chart(movies)
```

As you can see, the total gross and inflation adjusted gross fluctuates but at 
and after 2014, there was an increasing trend. Before 2014, the trend of the 
inflation adjusted gross were all larger than the trend of total gross to 
account. This is likely to account for the price level changes. But in 2014 and 
after, the inflation adjusted gross and total gross made the same gross values.

## How does the genre of a Disney movie affect the amount grossed?

This chart plots the relationship between the inflation adjusted gross over all 
the different genres of movies in the dataset. We made this box plot to see 
which genres grossed the most money for Disney.

```{r echo=FALSE}
box_plot_adjusted(movies)
```

This box plot shows that the Adventure and Musical categories make the most 
money on average. The genres making the lowest amount of money are Documentary 
and horror. Musical has an outlier that grossed far more than any other movie. 
The Y value of the graph plot was limited to make the plot readable.  


## What trends do we see in the top 20 highest-grossing Disney films in Disney history?

This bar chart compares the genres and ratings of the 20 highest-grossing 
films in Disney's history. We made it to see if there are any trends in which
types of movies do the best.

``` {r echo=FALSE}
make_3rd_chart(movies)
```

As we can see, the most popular, or highest-grossing, Disney films tend to 
fall in the adventure genre. These movies are also often rated G. In the 
earlier chart we did, we found that adventure movies are usually the 
highest-grossing. I think that from these charts we've made, we can infer that 
Disney has a good understanding of their audience. They clearly know that 
adventure movies make the most money so they stick to those. This chart can 
give us more confidence in our prior chart because we once again see that 
adventure films make a lot of money. 
