---
title: "Comparing Disney Films"
author: "Yuhaniz, Siya, Cole, Jonathan"
date: "11/25/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library("knitr")
source("chart3.R")
source("chart1.R")
source("summary_info.R")
```
## Introduction
Our domain of interest is entertainment so in this report, we'll be studying a 
data set comparing all of the movies made by Disney. We are interested in 
exploring the domain of entertainment because it is a very broad field with lots 
of available data in part due to the rise of streaming services. This data set 
includes all Disney movies up to 2016. It can be found [here](https://www.kaggle.com/prateekmaj21/disney-movies?select=disney_movies.csv).
We want to study this data to see what types of movies are the most successful 
in terms of grossing amount. These types of studies help Disney plan future 
films in terms of the genre, ratings etc. the film should stick to.

## Summary Info

This data displays a few aspects of Disney movies. Such as the release dates, 
genre, MPAA rating, total gross income and inflation adjusted gross income. In 
this data the highest gross movie is `r Highest_Gross_Movie` *Star Wars Ep. VII: 
The Force Awakens*. Also, the lowest gross movies would be the movies 
`r Lowest_Gross_Movies`. With this being said, the most common genre from the 
data are `r Most_Common_Genre` and the most common release date year would be 
the `r Most_Common_Release_Year`. Finally, in this data it displays 
`r Total_Movies`. This can all be seen below.
```{r}
summary
```


## Summary Table

This table shows 10 Disney movies with the average inflation gross income of 
each movie. Included with this is the genre of each of these movies and the MPAA 
rating. This demonstrates if the movie genre and the MPAA affects the inflation
gross income. 


## What trends do we see between the yearly gross of Disney movies over time?
This chart was intended to show the relationship between the yearly gross of 
Disney movies, comparing the inflation adjusted gross and total gross, over time 
from 1937 to 2016. We made it to see which years made the most movies gross.

```{r plot3, echo=FALSE, fig.width= 20}
plot_line_graph
```

As you can see, the total gross and inflation adjsuted gross flunctuates but at 
and after 2014, there was an increasing trend. Before 2014, the trend of the 
inflation adjusted gross were all larger than the trend of total gross to 
account. This is likely to account for the price level changes. But in 2014 and 
after, the inflation adjusted gross and total gross made the same gross values.


## What trends do we see in the top 20 highest-grossing Disney films in Disney history?
This bar chart compares the genres and ratings of the 20 highest-grossing 
films in Disney's history. We made it to see if there are any trends in which
types of movies do the best.

``` {r echo=FALSE}
make_3rd_chart(movies)
```

As we can see, the most popular, or highest-grossing, Disney films tend to 
fall in the adventure genre. These movies are also often rated G. In the 
earlier chart we did, we found that adventure movies are usually the 
highest-grossing. I think that from these charts we've made, we can infer that 
Disney has a good understanding of their audience. They clearly know that 
adventure movies make the most money so they stick to those. This chart can 
give us more confidence in our prior chart because we once again see that 
adventure films make a lot of money. 

