---
title: "Comparing Disney Films"
author: "Yuhaniz, Siya, Cole, Jonathan"
date: "11/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library("knitr")
source("chart3.R")
```
## Introduction
Our domain of interest is entertainment so in this report, we'll be studying a 
data set comparing all of the movies made by Disney. We are interested in 
exploring the domain of entertainment because it is a very broad field with lots 
of available data in part due to the rise of streaming services. This data set 
includes all Disney movies up to 2016. It can be found [here](https://www.kaggle.com/prateekmaj21/disney-movies?select=disney_movies.csv).
We want to study this data to see what types of movies are the most successful 
in terms of grossing amount. These types of studies help Disney plan future 
films in terms of the genre, ratings etc. the film should stick to.

## What trends do we see in the top 20 highest-grossing Disney films in Disney history?
This bar chart compares the genres and ratings of the 20 highest-grossing 
films in Disney's history. We made it to see if there are any trends in which
types of movies do the best.

``` {r echo=FALSE}
make_3rd_chart(movies)
```

As we can see, the most popular, or highest-grossing, Disney films tend to 
fall in the adventure genre. These movies are also often rated G. In the 
earlier chart we did, we found that adventure movies are usually the 
highest-grossing. I think that from these charts we've made, we can infer that 
Disney has a good understanding of their audience. They clearly know that 
adventure movies make the most money so they stick to those. This chart can 
give us more confidence in our prior chart because we once again see that 
adventure films make a lot of money. 
